\\textbf{Figure 3}

### 2022-10-05 Manuscript/Figures/Figure_2.Rmd
renaming figs

---
title: "\\textbf{Figure 2}"
output:
  pdf_document: default
  html_document: default
header-includes:
 - \usepackage{caption}
 - \captionsetup[figure]{labelformat=empty}
 - \captionsetup[table]{labelformat=empty}
---
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', out.width="100%"}

library(tidyverse)

@@

# Prepare top 20 records
top_20 <- data %>%
  filter(!Accepted_name == "Apis mellifera") %>%
  group_by(Accepted_name) %>%
  summarise(no_rows = length(Accepted_name)) %>%
  arrange(-no_rows) %>%
  slice(1:20)
# Fix row position
top_20$Accepted_name <- factor(top_20$Accepted_name, levels = top_20$Accepted_name)
# Plot
ggplot(top_20, aes(x = Accepted_name, y = no_rows)) +
  geom_bar(stat = "identity", fill = "#287D8EFF") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11, face = "italic"), axis.text.y = element_text(size=12),   axis.title=element_text(size=16), axis.line =element_line(size=1)) +
  ylab("Number of records") +
  xlab("Species") +
  scale_y_continuous(expand = c(0, 0))
```

>>>>

---
title: "\\textbf{Figure 2}"
output:
  pdf_document: default
  html_document: default
header-includes:
 - \usepackage{caption}
 - \captionsetup[figure]{labelformat=empty}
 - \captionsetup[table]{labelformat=empty}
---

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center',out.width="115%"}
library(sf)
library(raster)
library(rasterVis)
library(tidyverse)
library(data.table)
library(ggplot2)
library(viridis)
library(ggspatial)
library(ggsn)

@@

# Prepare data
data$Longitude <- as.numeric(data$Longitude)
data$Latitude <- as.numeric(data$Latitude)
data <- data %>% filter(!is.na(Latitude) & !is.na(Longitude))
# Keep points on balearic islands
data_1 <- data %>% filter(Province == "Balears, Illes")
data_1$Country_1 <- NA

# Filter points in Spain and Portugal
data$Country_1 <- NA
data$Country_1 <- maps::map.where(x = data$Longitude, y = data$Latitude)
data <- data %>% filter(Country_1 == "Spain" | Country_1 == "Portugal")
# Rbind points that are in Spain with the ones of Balearic islands
dat <- rbind(data, data_1)

#Plot map
world <- map_data("world")

ibera <- world %>% filter(region == "Spain" | region == "Portugal"| region == "France" |region == "Andorra"|region == "Marroco")

ggplot(data=dat, aes(Longitude, Latitude)) +
geom_map(data = ibera, map = ibera,
aes(long, lat, map_id = region), color = "white", fill = "grey", size = 0.1) +
geom_bin2d(bins=70, aes(fill=log(..count..))) +
theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
size = 0.5), panel.background = element_rect(fill = "aliceblue"),
panel.border = element_rect(colour = "black", fill=NA, size=1.5)) +
scale_fill_viridis() +
coord_sf(xlim = c(-9, 4), ylim = c(36, 44)) +
ggsn::north(x.min = -0.7, x.max = 3.3, 
y.min = 35.6, y.max = 37.6, scale = 0.4) +
scalebar(x.min = -2, x.max = 3.6,
y.min = 36.5, y.max = 42.5,
dist = 100, dist_unit = "km",st.size = 3,st.dist=0.04,
transform = TRUE, model = "WGS84", st.color="black") +
theme(axis.title = element_text(size=16), axis.text = element_text(size=12))

```

### 2022-10-05 Manuscript/Figures/Figure_3.Rmd
renaming figs

---
title: "\\textbf{Figure 3}"
output:
  pdf_document: default
  html_document: default
header-includes:
 - \usepackage{caption}
 - \captionsetup[figure]{labelformat=empty}
 - \captionsetup[table]{labelformat=empty}
---

```{r echo=FALSE, warning=FALSE, message=FALSE,fig.width=7,fig.height=6, fig.align='center',message=FALSE, warning=FALSE, cache=FALSE, out.width="100%"}

library(tidyverse)
data <- read.table("../../Data/iberian_bees.csv.gz", header = T, quote = "\"", sep = ",")

# Prepare top 20 records
by_year <- data %>% filter(!Accepted_name == "Apis mellifera")

p1 <- ggplot(by_year, aes(Year)) +
  geom_histogram(fill = "#287D8EFF") +
  theme_classic() +
  ylab("Number of records") +
  scale_y_continuous(expand = c(0, 0)) + ggtitle("A") + theme(axis.title=element_text(size=16), axis.text =element_text(size=12), axis.line =element_line(size=1),
plot.title = element_text(size=18, face = "bold"))

data$month_name <- month.abb[data$Month]

month_sum <- data %>%
  group_by(month_name) %>%
  summarise(no_rows = length(month_name)) %>%
  arrange(-no_rows)

month_sum <- month_sum %>% filter(!is.na(month_name))

month_sum$month_name <- factor(month_sum$month_name, levels = c(
  "Jan", "Feb", "Mar",
  "Apr", "May", "Jun",
  "Jul", "Aug", "Sep",
  "Oct", "Nov", "Dec"
))

p2 <- ggplot(data = month_sum, aes(x = month_name, y = no_rows)) +
  geom_bar(stat = "identity", fill = "#287D8EFF") +
  theme_classic() +
  scale_y_continuous(expand = c(0, 0)) +
  ylab("Number of records") +
  xlab("Months") + ggtitle("B") + theme(axis.title=element_text(size=16), axis.text =element_text(size=12), axis.line =element_line(size=1),
plot.title = element_text(size=18, face = "bold"))

library(patchwork)

p1 / p2
```

>>>>

---
title: "\\textbf{Figure 3}"
output:
  pdf_document: default
  html_document: default
header-includes:
 - \usepackage{caption}
 - \captionsetup[figure]{labelformat=empty}
 - \captionsetup[table]{labelformat=empty}
---
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', out.width="100%"}

library(tidyverse)

data <- read.table("../../Data/iberian_bees.csv.gz", header = T, quote = "\"", sep = ",")

# Prepare top 20 records
top_20 <- data %>%
  filter(!Accepted_name == "Apis mellifera") %>%
  group_by(Accepted_name) %>%
  summarise(no_rows = length(Accepted_name)) %>%
  arrange(-no_rows) %>%
  slice(1:20)
# Fix row position
top_20$Accepted_name <- factor(top_20$Accepted_name, levels = top_20$Accepted_name)
# Plot
ggplot(top_20, aes(x = Accepted_name, y = no_rows)) +
  geom_bar(stat = "identity", fill = "#287D8EFF") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 11, face = "italic"), axis.text.y = element_text(size=12),   axis.title=element_text(size=16), axis.line =element_line(size=1)) +
  ylab("Number of records") +
  xlab("Species") +
  scale_y_continuous(expand = c(0, 0))
```
